Learning from Massive Noisy Labeled Data for Image Classification

### 2015-04-13 paper.tex
Update paper.tex
Update abstract

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems. However, obtaining a massive amount of well labeled data is usually very expensive and time consuming. In this paper, we introduce a general framework to train CNNs with only a limited number of clean labels and millions of easily obtained noisy labels. We describe label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system. To demonstrate the effectiveness of our approach, we collect a large-scale clothing classification dataset with both noisy and clean labels. Experiments on this dataset show that our model can better detect and correct the wrong labels, which benefits the training of underlying CNNs.
\end{abstract}

>>>>

%%%%%%%%% ABSTRACT
\begin{abstract}
Large-scale supervised datasets are crucial to train convolutional neural networks (CNNs) for various computer vision problems. However, obtaining a massive amount of well-labeled data is usually very expensive and time consuming. In this paper, we introduce a general framework to train CNNs with only a limited number of clean labels and millions of easily obtained noisy labels. We model the relationships between images, class labels and label noises with a probabilistic graphical model and further integrate it into an end-to-end deep learning system. To demonstrate the effectiveness of our approach, we collect a large-scale real-world clothing classification dataset with both noisy and clean labels. Experiments on this dataset indicate that our approach can better correct the noisy labels and improves the performance of trained CNNs. 
\end{abstract}
